Paper Report

### 2017-11-23 Paper_report.tex
Save

%----------------------------------------------------------------------------------------
%	Alignment by agreement
%----------------------------------------------------------------------------------------
\section{Alignment by Agreement \citep{Liang2006Alignment}}

@@

\paragraph{How to apply NN ?}
\begin{itemize}
\item Emission matrix $p_{\theta}(f_j | e_{a_j})$: It is not the normal way of translation. We receive the target-language sentence and return the probabilities of all source-language vocabulary.
\item Transition matrix $p_{\theta}(a_j | a_{j-1})$: We receive the target-language sentence and return this matrix.
\item The posteriors $p_{\theta'}(a_j|f_j)$ and $p_{\theta'}(a_j, a_{j-1}|f_j)$ : We set source-language sentence as a set of observation, Baum-Welch algorithm returns forward and backward messages (How is the size of these messages)
\end{itemize}

\subsection{Non-probability - Score approach}
The papers are \cite{Yang13word}, \cite{Tamura14recurrent}.

>>>>

%----------------------------------------------------------------------------------------
%	Alignment by agreement
%----------------------------------------------------------------------------------------
\section{Alignment by Agreement \citep{Liang2006Alignment}}
\subsection{Main idea}
This approach is similar to ensemble method. In this unsupervised approach, the two simple asymmetric models are trained jointly to maximize a combination of data likelihood and agreement between the models. The new point is encouraging the agreement between these models during training.

In fact, intersecting the alignment prediction of two asymmetric models reduces AER. An assumption is that this intersection (Agreement) could reduce the loss of each asymmetric model.

Moreover, we could see the transformation from asymmetric models to symmetric model.

\subsection{}

@@

\paragraph{How to apply NN ?}
\begin{itemize}
\item Emission matrix $p_{\theta}(f_j | e_{a_j})$: It is not the normal way of translation. We receive the target-language sentence and return the probabilities for all source-language vocabulary.
\item Transition matrix $p_{\theta}(a_j | a_{j-1})$: We receive the target-language sentence and return this matrix.
\item The posteriors $p_{\theta'}(a_j|f_j)$ and $p_{\theta'}(a_j, a_{j-1}|f_j)$ : We set source-language sentence as a set of observation, Baum-Welch algorithm returns forward and backward messages (How is the size of these messages)
\end{itemize}

\paragraph{What is the problem of transition matrix in programming ?}
The input of transition model is target sentence. The model returns the matrix with its size being ($I * I$).

However, this matrix is hard to return. This is why I return matrix ($I * V_e$) with $V_e$ is the size of target language vocabulary. From this matrix, I could select the probabilities of the words existed in target sentence. The final result is a matrix with its size being ($I * I$).

This method breaks the structure of the tensor tree. The cost calculated can not be back-propagated because there is no relationship between this cost and this matrix ($I * V_e$).

\subsection{Non-probability - Score approach}
\subsubsection{\cite{Yang13word}, \cite{Tamura14recurrent}}

\section{Symmetrical alignment}
